### 2020-05-03 Paper/paper.tex

This project takes data from galactic models and associated
human fitness scores, with the goal to develop both a single layer 
neural net and a convolutional neural net that will help scientists better understand this
data. These two nets will be used to produce a machine fitness score for each model image
that we hope will closely match its respective human fitness score. We will compare these two networks based on how well they were able to match human scores with their predictions.
By having theses tools like these neural networks, scientists can
quicken the search to find those well-fitting models, explore
the galactic model parameter space, and hopefully find the
true dynamic parameters for observable galaxy collisions.

>>>>

This project takes data from galactic models and associated
human fitness scores, with the goal to develop both a single layer 
neural net and a convolutional neural net that will help scientists better understand this
data. These two nets will be used to produce a machine fitness score for each model image
that we hope will closely match its respective human fitness score. We will compare these two networks based on how well they were able to match human scores with their predictions.
By having tools like these neural networks, scientists can
quicken the search to find those well-fitting models, explore
the galactic model parameter space, and hopefully find the
true dynamic parameters for observable galaxy collisions.
